MLH1 Results Outline

### 2020-02-23 doc/Results.rmd
small changes

musc and mol ttests
mol p = `r Q2tot.sc_t.test_High.Low_Mol$p.value` Mole have significant difference between mouse means

@@

Thse are our prediction for the glm models based on the variation of the gwRR's

@@

@@

the different lack of predictive power of SC length to predict CO number -- indicates that there might be different patterns of 'SC usage' / different patterns in the layout of the recombination landscape /  these patterns could stem from placement or spacing of foci.

@@

The previous section found that the single crossover landscape is significantly different between males and females.
In this section -- we focus on differences between the high and the low rec male strains
In order to test if if there are distinguishing meterics for these two groups.

@@

The first use t.tests to test if there are significant differences in the single CO landscapes between the high and low rec groups.

T tests of the single crossover positions reveal that the normalized 1 foci positions are not significantly different between the total pooled high and low rec male strains (t.test; p = `r Rec.group_BivData_F1post_Ttest$p.value`).

further tests -- within the subspecies, musculus and molossinus,

@@

 -- BUT this might be due to sampling for MSM -- but it doesn't seem to be the case in MOLF,

(MSM and MOLF have different proportions of chromosome classes -- (MSM has the smallest propotion of 1COs, across the strains, BUT the mean and distributions for MSM of single foci positions are equivilent across all the strains.

Where as something is

@@

>>>>

musc and mol ttests
mol p = `r Q2tot.sc_t.test_High.Low_Mol$p.value` Mole have significant difference between mouse means for total sc, between the high and low srains

@@

Thse are our prediction for the M3 glm (just straint) models based on the variation of the gwRR's

@@

- th predictions for M3 (strain) differencs (motivated by the gwrr variation are not met,  (correlation of SC means and CO means?))

@@

the lack of predictive power of SC length to predict CO number indicates that there might be different patterns of 'SC usage' / different patterns in the layout of the recombination landscape /  these patterns could stem from placement or spacing of foci.

@@

The previous section found that the single crossover landscape is significantly different between males and females.
In this section we focus on differences between the high and the low rec male strains
In order to test if if there are distinguishing meterics for these two groups.

@@

T tests of the single crossover positions reveal that the normalized single foci positions are not significantly different between the total pooled high and low rec male strains (t.test; p = `r Rec.group_BivData_F1post_Ttest$p.value`).

<further tests -- within the subspecies, musculus and molossinus?

@@

 <BUT this might be due to sampling for MSM -- but it doesn't seem to be the case in MOLF, 
 (MSM and MOLF have different proportions of chromosome classes -- (MSM has the smallest propotion of 1COs, across the strains, BUT the mean and distributions for MSM of single foci positions are equivilent across all the strains.>

@@

in addition models which use mouse average of foci position as a dependat variable, we decided to run models for the single bivalent level, and which include chromosome length as a fixed effect.
